% Other XML testing frameworks
%
% Author: Filip van Laenen <f.a.vanlaenen@ieee.org>
% Version: $Id: chpt_other_xml_testing_frameworks.tex 18 2009-04-14 18:13:25Z filipvanlaenen $

\chapter{Other XML Testing Frameworks}

\section{Jeni Tennison's XSLT Unit Testing Utilities}

Jeni Tennison\seeurl{http://www.jenitennison.com/xslt/utilities/unit-testing}

Hacked together at a summer school in 2005, as an XP experiment.

\begin{quotation}
I've heard a lot about XP over the last few years, but never really got into the whole unit testing thing: I think that like a lot of programmers, I viewed writing tests as too much hard work. But during this summer (2005), I'm working on a project that's using an XP development methodology, plus Tim Bray talked glowingly about XP and unit testing during his talk about the XML Summer School. I decided that if I was going to do unit testing, I needed it to be really easy to write and run the tests.

So during the remaining couple of days at the XML Summer School, I hacked up the solution you see here. I tried to remain true to the rest of the XP philosophy: this does the minimum of what I need it to do at the moment, and if I find I need it to do more, then I'll add the code to do it.
\end{quotation}

\section{Juxy}

Juxy\seeurl{http://juxy.tigris.org}

Tests written in Java

\section{UTF-X}

UTF-X\seeurl{http://utf-x.sourceforge.net}

Version number is 0.0.8, written in August 2006, lots of syntactic sugar

\section{XMLUnit}

XMLUnit\seeurl{http://xmlunit.sourceforge.net}

Does only the comparison of XML documents: you have to build the transformation in yourself in the code.
May be usefull to do the XML comparison in TestXNG.

\section{XSLTUnit}

XSLTUnit\seeurl{http://xsltunit.org}

Written in 2002/2003, tests are XSL transformations, lots of syntactic sugar